---
title: "Dataset report of a burrow data file"
author: "Suzanne Fox"
date: "February 2017"
output: word_document
df_print: kable
---

```{r setup, echo=FALSE,  message=FALSE, warning=FALSE}

knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
#library(cowplot)

workdir <- "C:/Users/Suzanne/OneDrive - Suzanne Fox/Dissertation/R/"

setwd(workdir)

Data.source <- read.csv("TestData.csv", stringsAsFactors = FALSE)
Data.burrow <- read.csv("TestBurrow.csv", stringsAsFactors = FALSE)

```

## Dataset details


```{r structure, echo=FALSE, comment="", collapse=TRUE}
# Dataset name
Data.name <- subset(Data.burrow, InfoLevel=="DATASET" &  InfoType=="SOURCEDATA",
c("InfoDetail"))
cat(paste("Source data name -", Data.name))

# Description
Data.description <- subset(Data.burrow, InfoLevel=="DATASET" & InfoType=="SOURCE",
c("InfoDetail"))
cat(paste("Source data description -", Data.description))

# Run time
Data.rundate <- subset(Data.burrow, InfoLevel=="HEADER" & InfoType=="RUN DATE",
c("InfoDetail"))
cat(paste("Burrow data created -", Data.rundate))

# Dataset structure ================================================

numcols <- subset(Data.burrow, Variable1=="NUMCOLS", c("myData1"))
numrows <- subset(Data.burrow, Variable1=="NUMROWS", c("myData1"))
outtext <- sprintf("Dataset dimensions - %s columns (variables) and %s rows (cases)",numcols, numrows)

cat(outtext)
```

## Best Guess at datatype for each variable


```{r datatypes, echo=FALSE, comment="", collapse=TRUE}
Data.bestguess <- subset(Data.burrow, InfoType=="BEST GUESS", select=c("Variable1","myData1"))
names(Data.bestguess) <- c("Variable","Datatype")

print(Data.bestguess, row.names=FALSE)

```

# print(burrow.report)

# # Visualise Uniques
# p1 <- ggplot(data=burrow.report, 
#        aes(x=VariableName, y=Unique)) +
#        geom_bar(colour="black", fill="#4C1E9C", 
#                 width=.8, stat="identity") + 
#                 guides(fill=FALSE) +
#                 xlab("Variables") + ylab("% of Total") +
#                 ggtitle("Unique Values") +
#                 ylim(0, 100) +
#               theme(panel.grid.major = element_blank(), 
#               panel.grid.minor = element_blank(),
#               panel.background = element_blank(), 
#               axis.line=element_blank(),
#               axis.text.x=element_blank(),
#               axis.text.y=element_blank(),
#               axis.ticks=element_blank(),
#               legend.position="none")
# 
# 
#   # Visualise Missing
# p2 <-  ggplot(data=burrow.report, 
#          aes(x=VariableName, y=Missing)) +
#          geom_bar(colour="black", fill="#4C1E9C", 
#                   width=.8, stat="identity") + 
#                   guides(fill=FALSE) +
#                   xlab("Variables") + ylab("% of Total") +
#                   ggtitle("Missing Values") +
#                   ylim(0, 100) +
#           theme(panel.grid.major = element_blank(), 
#                 panel.grid.minor = element_blank(),
#                 panel.background = element_blank(), 
#                 axis.line=element_blank(),
#                 axis.text.x=element_blank(),
#                 axis.text.y=element_blank(),
#                 axis.ticks=element_blank(),
#                 legend.position="none")
# 
# # plot uniques and missings
# plot_grid(p1, p2, align='h')
# 
# if (sum(burrow.report$Missing)==0) {
#   print("There were no missing values for any variable")
# } else {
#   print("Dealing with missing data")
# }
# 
# #plotvar <- "mpg"
# #myPlot_Int(mtcars,plotvar)
# 
# num.histograms <- nrow(burrow.plothist)
# print(paste("There are",num.histograms,"numeric fields."))
# 
# for (i in seq_len(num.histograms)) {
#   plotvar <- burrow.plothist[i,c("VariableName")]
#   print(paste("Plotting",plotvar))
# 
#   possibleError <- tryCatch(
#     myPlot <- myPlot_Int(burrow.inputdata,plotvar),
#     error=function(e) e
#   )
# 
#   if(inherits(possibleError, "error")) {
#     print(paste("error plotting",plotvar))
#     next
#   }
# 
#   print(myPlot)
# }

